---
title: "Sample Report"
author: "Helper Bryan"
date: "2024-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# My Summary of Today

**This R workshop was so long but I learned something!**

## How I feel about things

*Thank goodness tomorrow is Friday.*

### Working with R is fun

`This is cool-looking code.`

A numeric list:

1.  It is relatively easy to use (?)
2.  It provides lots of functionality for dat vis.
3.  There is no number 3.

A bulletted list: (need a blank line before the list)

-   asterisk or dash creates a bulletted item
-   thing 2
-   there is no third item

[Center for Teaching Excellence](https://cte.rice.edu/)

### Loading Data and Libraries:

```{r load_data_and_libraries}
gapminder <- read.csv(file = "../data/gapminder_data.csv", stringsAsFactors = TRUE)
library(ggplot2)
library(dplyr)
```

### Basic plot

```{r plot_data}
ggplot(data = gapminder,
       mapping = aes(x = pop, y = lifeExp)) +
  geom_point(alpha=0.3)
```

`r 2 + 2`

```{r variable_underscore_definition, echo = FALSE, results = "hide"}
US_2007 <- gapminder %>%
  filter(country == "United States", year == 2007)
options(scipen = 999)
```

The US gross domestic product per capita is `r US_2007$gdpPercap`.